Reanalysis Step 2: Multiple Imputation (Clean Version)

### 2025-08-29 reanalysis-2-multiple_imputation.qmd
more predictor

# Fellow-eye predictors with weight=2 for stronger influence
fellow_vars <- c("fellow_baseline_VA", "fellow_intermediate_VA", "fellow_outcome_VA", "fellow_dr")
for (v in fellow_vars) {
  if (v %in% rownames(pred_matrix)) {
    pred_matrix[v, ] <- 0
  }
}
if ("fellow_baseline_VA" %in% colnames(pred_matrix)) {
  pred_matrix["baseline_VA_logMAR", "fellow_baseline_VA"] <- 2  # Weight=2
}
if ("fellow_intermediate_VA" %in% colnames(pred_matrix)) {
  pred_matrix["intermediate_VA_logMAR", "fellow_intermediate_VA"] <- 2  # Weight=2
}
if ("fellow_outcome_VA" %in% colnames(pred_matrix)) {
  pred_matrix["outcome_VA_logMAR", "fellow_outcome_VA"] <- 2  # Weight=2
}
if ("fellow_dr" %in% colnames(pred_matrix) && "person_dr" %in% rownames(pred_matrix)) {
  pred_matrix["person_dr", "fellow_dr"] <- 2  # Weight=2
}

>>>>

# Ensure demographics predict VA timepoints and DR severity
va_vars <- c("baseline_VA_logMAR", "intermediate_VA_logMAR", "outcome_VA_logMAR", "person_dr")
for (va in va_vars) {
  for (demo in demographic_vars) {
    if (va %in% rownames(pred_matrix) && demo %in% colnames(pred_matrix)) {
      pred_matrix[va, demo] <- 1
    }
  }
}

# Ensure ocular comorbidities and cataract surgery predict VA and DR severity
ocular_vars <- c("glaucoma_bef_hitplus_cat", "otherretina_bef_hitplus_cat", "catsurg_before_hitplus_cat")
for (va in va_vars) {
  for (ov in ocular_vars) {
    if (va %in% rownames(pred_matrix) && ov %in% colnames(pred_matrix)) {
      pred_matrix[va, ov] <- 1
    }
  }
}

# Ensure treatments predict intermediate and outcome VA
for (va in c("intermediate_VA_logMAR", "outcome_VA_logMAR")) {
  for (tr in treatment_vars) {
    if (va %in% rownames(pred_matrix) && tr %in% colnames(pred_matrix)) {
      pred_matrix[va, tr] <- 1
    }
  }
}

# Fellow-eye predictors with weight=2 for stronger influence
fellow_vars <- c("fellow_baseline_VA", "fellow_intermediate_VA", "fellow_outcome_VA", "fellow_dr")
for (v in fellow_vars) {
  if (v %in% rownames(pred_matrix)) {
    pred_matrix[v, ] <- 0
  }
}
if ("fellow_baseline_VA" %in% colnames(pred_matrix)) {
  pred_matrix["baseline_VA_logMAR", "fellow_baseline_VA"] <- 1
}
if ("fellow_intermediate_VA" %in% colnames(pred_matrix)) {
  pred_matrix["intermediate_VA_logMAR", "fellow_intermediate_VA"] <- 1
}
if ("fellow_outcome_VA" %in% colnames(pred_matrix)) {
  pred_matrix["outcome_VA_logMAR", "fellow_outcome_VA"] <- 1
}
if ("fellow_dr" %in% colnames(pred_matrix) && "person_dr" %in% rownames(pred_matrix)) {
  pred_matrix["person_dr", "fellow_dr"] <- 1
}
